Estimating Access to Rabies Post-Exposure Prophylaxis in Madagascar

### 2019-01-08 accessPEP.Rmd
added in taking out contacts by distribution of patients per day
Going to probably leave this out though...

ctar_check %>%
  group_by(id_ctar) %>%
  summarize(prop_excluded = length(exclude_bydate[exclude_bydate == 1])/n()) %>%
  ggplot(data = ., aes(y = id_ctar, prop_excluded)) +
  geom_point()

>>>>

ctar_check %>%
  group_by(id_ctar) %>%
  summarize(prop_excluded = length(exclude_bydate[exclude_bydate == 1])/n()) -> summ_check

#   ggplot(data = ., aes(y = id_ctar, prop_excluded)) +
#   geom_point()
